Is it time for an NBA expansion?

### 2024-04-15 paper/paper.qmd
.

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
madal <- lm(PTS ~ Year + Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)

# Summary of the linear model
msummary(
  list(
    "times" = nba_model,
    "plus" = madal
  ),
  fmt = 2
  )

>>>>

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams^2 + AST^2 + TRB^2 + STL + BLK + TOV, data = sim_nba_data)
model_ny <- lm(PTS ~ Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)

# Summary of the linear model
msummary(
  list(
    "With Year" = nba_model,
    "Without Year" = model_ny
  ),
  fmt = 2
  )
